\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-05-01 doc/USER_MANUAL/copyright_and_version.tex
removed old copy of AxiSEM, as requested by several developers (there was no reason to have one, and it was making the code more complex for no reason)

MPI v. 3.0, December 2014: many developers.
Convolutional PML, LDDRK time scheme, bulk attenuation support, simultaneous MPI runs,
ADIOS file I/O support, coupling with external codes, new seismogram names,
Deville routines for additional GLL degrees, tomography tools, unit/regression test framework,
improved CUDA GPUs performance, additonal GEOCUBIT support, better make compilation,
git versioning system. \\

>>>>

MPI v. 3.0, December 2014: many developers.
Convolutional PML, LDDRK time scheme, bulk attenuation support, simultaneous MPI runs,
ADIOS file I/O support, new seismogram names,
Deville routines for additional GLL degrees, tomography tools, unit/regression test framework,
improved CUDA GPUs performance, additonal GEOCUBIT support, better make compilation,
git versioning system. \\
